Automated Synthesis of State-Space Digital Systems

### 2016-12-20 cav2017/cav2017.tex
Table

>>>>

\begin{table}[]
\centering
\footnotesize
\caption{Test suite for space-state synthesis}
\label{State-space benchmarks}
\begin{tabular}{|c|c|c|c|c|}
\hline
%\textbf{ID \#} & 
\textbf{System}                                                               & \textbf{A} & \textbf{B} & \textbf{C} & \textbf{D} \\ \hline
%1              & 
\begin{tabular}[c]{@{}c@{}}DC Motor\\ Position\end{tabular}                   & $\left[\begin{array}{ccc}
0		& 1 		& 0						\\
0 		& -1.087	& 8587					\\
0		& -9964		& -1.455\times 10^{6}	\\
\end{array}\right]$ & $\left[\begin{array}{c}
0 \\ 0 \\ -1.455\times10^{6}
\end{array}\right]$           & $\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right]$ & 0 \\  \hline
%2              & 
\begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
-0.313	& 56.7 		& 0		\\
-0.0139	& -0.426	& 0		\\
0		& 56.7		& 0		\\
\end{array}\right]$ & $\left[\begin{array}{c}
0.232 \\ 0.0203 \\ 0
\end{array}\right]$ & $\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right]$ & 0 \\ \hline
%3            & 
\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
0		& 1 		& 0		\\
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
\end{array}\right]$ & $\left[\begin{array}{c}
0 \\ 0 \\ 1.923
\end{array}\right]$ & $\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right]$ & 0 \\ \hline
%4              & 
\begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
\end{array}\right]$ & $\left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]$ & $\left[\begin{array}{cc}
 0 & 1\\
\end{array}\right]$ & 0 \\ \hline
%5              & 
\begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
0		& -375 \\
3409	& -1515\\
\end{array}\right]$ & $\left[\begin{array}{c}
500 \\ 0 \\
\end{array}\right]$ &  $\left[\begin{array}{cc}
0 & 1\\
\end{array}\right]$  & 0        \\ \hline
%6              & 
\begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
\end{array}\right]$ & $\left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]$ & $\left[\begin{array}{cc}
0 & 1\\
\end{array}\right]$ & 0 \\ \hline
%7              & 
\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & -0.05 & 0.03125 & 0.032 & 0 \\ \hline
%8              & 
\begin{tabular}[c]{@{}c@{}}DC Motor\\ Rate\end{tabular} & $\left[\begin{array}{cc}
-1000		& -13 \\
-8			& 0\\
\end{array}\right]$ & $\left[\begin{array}{c}
4 \\ 0 \\
\end{array}\right]$ & $\left[\begin{array}{cc}
0 & 6.25\\
\end{array}\right]$ & 0 \\ \hline
%9              & 
\begin{tabular}[c]{@{}c@{}}Helicopter\\ Longitudinal\\ Motion\end{tabular}    & $\left[\begin{array}{ccc}
-0.42		& 0.0168		& -0.396	\\
0.5			& 0				& 0			\\
0			& 0.5 			& 0			
\end{array}\right]$ & $\left[\begin{array}{c}
16 \\ 0 \\ 0
\end{array}\right]$ & $~
\left[\begin{array}{ccc}
0.6125	& -0.6125	& 15.44 \\
\end{array}\right]$ & 0 \\ \hline
%10             & 
Pendulum   & $\left[\begin{array}{cc}
0		& -2.453	\\
4		& 0			\\	
\end{array}\right]$ & $\left[\begin{array}{c}
4 \\ 0
\end{array}\right]$ & $\left[\begin{array}{cc}
-1.225	& -2.15 	\\
\end{array}\right]$           & 9.8           \\ \hline
%11             & 
\begin{tabular}[c]{@{}c@{}}Inverted\\ Pendulum\end{tabular} & $\left[\begin{array}{cccc}
0		& 1		& 0 	& 0	\\
1		& 0		& 0		& 0	\\
0		& 1 	& 0		& 0 \\
0		& 0		& 1 	& 0 \\	
\end{array}\right]$ & $\left[\begin{array}{c}
1 \\ 0 \\ 0 \\ 0
\end{array}\right]$  & $\left[\begin{array}{cccc}
0	& 0	& 1 & -0.75 \\
0	& 1	& 0	& 0		
\end{array}\right]$ & $\left[\begin{array}{c}
0 \\
0 \end{array}\right]$ \\ \hline
%12             & 
\begin{tabular}[c]{@{}c@{}}Magnetic\\ Suspension\end{tabular} & $\left[\begin{array}{cc}
0		& 31.25	\\
32		& 0		\\	
\end{array}\right]$ & $\left[\begin{array}{c}
8 \\ 0
\end{array}\right]$ & $\left[\begin{array}{cc}
0	& 9.766 	\\
\end{array}\right]$ & 0 \\ \hline
%13             & 
\begin{tabular}[c]{@{}c@{}}Magnetic\\ Pointer \end{tabular} & $\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0	\\
0			& 0.01562 	& 0	\\	
\end{array}\right]$ & $\left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]$ & $\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right]$ & 0           \\ \hline
%14             & 
\begin{tabular}[c]{@{}c@{}}1/4 Car\\ Suspension\end{tabular} & $
\left[\begin{array}{cccc}
-516.1	& -222.1& -79.75& -33.06	\\
256		& 0		& 0		& 0			\\
0		& 64 	& 0		& 0 \\
0		& 0		& 32 	& 0 \\	
\end{array}\right]$ & $\left[\begin{array}{c}
8 \\ 0 \\ 0 \\ 0
\end{array}\right]$ & $\left[\begin{array}{cccc}
0	& 0	& 9.969 & 4.133 \\
\end{array}\right]$ & 0 \\ \hline
%15             & 
\begin{tabular}[c]{@{}c@{}}Computer\\ Tape\\ Driver\end{tabular} & $\left[\begin{array}{ccc}
-1760		& -976.6	& -457.8	\\
1024		& 0			& 0			\\
0			& 512 		& 0			\\	
\end{array}\right]$ & $\left[\begin{array}{c}
8 \\ 0 \\ 0
\end{array}\right]$ & $\left[\begin{array}{ccc}
1.5	& 2.051	& 1.144 \\
\end{array}\right]$ & 0           \\ \hline
%16             & 
\begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0			\\
0			& 0.01562 	& 0			\\	
\end{array}\right]$ & , $\left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]$ & $\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right]$ & 0 \\ \hline
\end{tabular}
\end{table}
